Sparse Function-space Representation of Neural Networks

### 2023-05-30 workshop/main.tex
typo
fixed table ref

\begin{abstract}
Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting. We present a method that mitigates these issues by converting neural networks from weight-space to a low-rank function-space representation, via the so-called dual parameters. In contrast to previous work, our sparse representation captures the joint distribution over the entire data set, rather than only over a subset. This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance. We provide proof-of-concept demonstrations with the proposed approach for quantifying uncertainty in supervised learning on UCI benchamark tasks.
\end{abstract}

@@

\section{Discussion and conclusion}
\label{sec:conclusion}
%
In this paper, we have introduced \our, a novel approach for representing neural networks in sparse function space, exploiting the dual parameters for an efficient low-rank approximation that accommodates information from the entire data distribution. Our method offers a powerful mechanism for capturing predictive uncertainty, opens up new possible avenues for updating the model with new data without retraining, and providing a compact representation suitable for continual learning. In this workshop paper, we showcased our method's ability to capture uncertainty in UCI benchmark classification tasks (\cref{sec:uci}). The appealing properties of \our should make it a good addition to the tool set of modelling in sequential learning settings, such as continual and reinforcement learning. 
%These aspects were demonstrated in a wide range of problems, data sets, and learning contexts. We showcased our method's ability to capture uncertainty in UCI classification tasks (\cref{sec:uci}), demonstrated robustness on image data sets (\cref{,sec:image}), established its potential for continual learning (\cref{sec:cl-exp}), and finally, verified its applicability in reinforcement learning scenarios (\cref{sec:rl-exp}).

>>>>

\begin{abstract}
Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting. We present a method that mitigates these issues by converting neural networks from weight-space to a low-rank function-space representation, via the so-called dual parameters. In contrast to previous work, our sparse representation captures the joint distribution over the entire data set, rather than only over a subset. This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance. We provide proof-of-concept demonstrations with the proposed approach for quantifying uncertainty in supervised learning on UCI benchmark tasks.
\end{abstract}

@@

\section{Discussion and conclusion}
\label{sec:conclusion}
%
In this paper, we have introduced \our, a novel approach for representing neural networks in sparse function space, exploiting the dual parameters for an efficient low-rank approximation that accommodates information from the entire data distribution. Our method offers a powerful mechanism for capturing predictive uncertainty, opens up new possible avenues for updating the model with new data without retraining, and providing a compact representation suitable for continual learning. In this workshop paper, we showcased our method's ability to capture uncertainty in UCI benchmark classification tasks (\cref{tbl:uci}). The appealing properties of \our should make it a good addition to the tool set of modelling in sequential learning settings, such as continual and reinforcement learning.
%These aspects were demonstrated in a wide range of problems, data sets, and learning contexts. We showcased our method's ability to capture uncertainty in UCI classification tasks (\cref{sec:uci}), demonstrated robustness on image data sets (\cref{,sec:image}), established its potential for continual learning (\cref{sec:cl-exp}), and finally, verified its applicability in reinforcement learning scenarios (\cref{sec:rl-exp}).
